Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-29 forecast/paper/supplement.Rmd
Update supplement with comparison figures

>>>>

<!-- Comparison to the Hub -->

```{r compare-to-hub, fig.cap="Performance of the AR model re-estimated for state-level, epiweek case incidence. The thin grey lines are the forecasts of other teams."}
knitr::include_graphics("fig/compare-states-to-hub.pdf")
```

```{r state-level-performance, fig.cap="Performance of our models re-estimated for state-level, epiweek case incidence."}
knitr::include_graphics("fig/state-level-performance.pdf")
```

### 2021-10-29 forecast/paper/supplement.tex
Update supplement with comparison figures

>>>>

{\centering \includegraphics[width=\textwidth]{fig/compare-states-to-hub}

\caption{Performance of the AR model re-estimated for state-level, epiweek case incidence. The thin grey lines are the forecasts of other teams.}\label{fig:compare-to-hub}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/state-level-performance}

\caption{Performance of our models re-estimated for state-level, epiweek case incidence.}\label{fig:state-level-performance}
\end{figure}
